---
title: "p8105_hw1_sc5352.Rmd"
author: "Chrissy Chen"
date: "2023-09-17"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r installpackage}
library(moderndive)
library(tidyverse)
```

```{r problem1}
data = get("early_january_weather")
data
```

### Descrption  
The dataset has `r nrow(data)` rows and `r ncol(data)` columns. The mean temperature is `r mean(data$temp)`. Variables are `r variable.names(data)` (origin, year, month, day, hour, temperature, dewpoint, humidity, wind direction and wind speed). Notice that temperature reaches the lowest point at 6 and highest at 10. Also, wind speed is lowest at 2 and highest at 7 and 9.   

### Scatterplot

```{r}
scatterplot = ggplot(data, aes(x = time_hour, y = temp, color = humid)) + geom_point()
scatterplot
ggsave("scatterplot.pdf", plot = scatterplot)
```

In this plot, the overall temperature increases and reaches a temporary peak on Jan 14th. Also, the humidity is high around Jan 14th.  

## Problem 2
```{r problem2}
df = tibble(
  vec_num = rnorm(10),
  vec_logical = vec_num > 0,
  vec_char = c("1","2","3","4","5","6","7","8","9","0"),
  vec_factor = factor(c("high","median","low","high","median","low","high","median","low","high"))
)
df
```

```{r, warning=FALSE, results='hide'}
mean(df$vec_num)
mean(as.numeric(df$vec_logical))
mean(as.numeric(df$vec_char))
mean(as.numeric(df$vec_factor))
```


The `mean` function works for the numerical and logical variables, but not for the character and factor vectors. The reason might be that character and factor vectors do not have the numerical meanings. After using `as. numeric` function, I can calculate all four means since this function changes data type into something calculable.
